---
title: "GSS challange More Data"
author: "Karen Gomez"
date: "Summer 2023"
output: html_document
---

```{r include=FALSE,echo=FALSE}
source(file="fisherXY.R")
require(tidyverse)
require(tigerstats)
require(knitr)
require(foreign)
GSS <-read.dta(file="GSS2016.dta")
GSS <- droplevels(GSS)
mydata <- select(GSS,race,cappun)
mydata <- na.omit(mydata)
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

Is attitude toward capitol punishment (cappun) independent of race (race)?
If not, then whose view differs from whom??

```{r eval=FALSE}
mydata <- mydata %>%
mutate(across(where(is.character), as.factor))
```

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

I’m going to be using the cat cat helper file, like numerical,graphical,and inferential, so I can figure out if capital punishment depends on race.

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->

```{r}
barchartGC(~race + cappun,data=mydata)
barchartGC(~race + cappun,data=mydata, type="percent")

```

The plot shows that there are about 1450 white people who are in favor for capital punishment and about 550 White people who are opposed capital punishment and about 250 black people are for capital punishment and about 350 black people are against capital punishment or we could say 65% of white people are for it and 35% of white people who are against it, about 45% of black people are for capital punishment and about 55% of black people are against capital punishment. The white people are for it 2 to 1 and for black people it is 5 to 4. 

## Now with The Most data (fewer variables gives more data points)



### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
table1 <- xtabs(~race + cappun, data=mydata)
rowPerc(table1)
colPerc(table1)
```

The white people are 65% for it and 35% against it, Black people are 43% for it and 57% against it, for other people there are 55% for it and 45% against it. The biggest split is with the white and the black.

## Now with More data



## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

`


## More data version


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
